A Tutorial on Tailored Simulation-Based Sample Size Planning for Experimental Designs with Generalized Linear Mixed Models

### 2024-11-05 _manuscript/_tex/manuscript.tex
fix precision result figure labels

\begin{tcolorbox}[enhanced jigsaw, leftrule=.75mm, arc=.35mm, colframe=quarto-callout-important-color-frame, toprule=.15mm, colback=white, title=\textcolor{quarto-callout-important-color}{\faExclamation}\hspace{0.5em}{Important}, bottomtitle=1mm, opacitybacktitle=0.6, colbacktitle=quarto-callout-important-color!10!white, left=2mm, opacityback=0, rightrule=.15mm, breakable, coltitle=black, toptitle=1mm, titlerule=0mm, bottomrule=.15mm]

@@

To our knowledge, existing approaches for sample size planning for GLMMs
have exclusively focused on planning for power. In Table 1, we review
available software packages that can be used to perform power analysis
for multilevel models in R {[}Version 4.3.3; R Core Team
(\citeproc{ref-R-base}{2024}){]}. Power analysis methods can be
categorized into formula-based, summary-statistics-based and
simulation-based methods
(\citeproc{ref-murayamaSummarystatisticsbasedPowerAnalysis2022}{Murayama
et al., 2022}). Formula-based methods rely on exact formulas to
calculate power directly. Summary-statistics-based methods use
statistical theory to approximate power based on formula-based methods
developed for simple t-tests. Simulation-based methods rely on
repeatedly simulating data with a known true effect size and estimating
power empirically, that is what percentage of simulated datasets
produces a significant p-value. Available formula-based and
summary-statistics-based software packages for multilevel models often
do not include GLMMs or are limited to simple designs
(\citeproc{ref-murayamaSummarystatisticsbasedPowerAnalysis2022}{Murayama
et al., 2022};
\citeproc{ref-westfallStatisticalPowerOptimal2014}{Westfall et al.,
2014}), making it necessary to build data simulations tailored
specifically to the study design. A number of tutorials have been
published describing how to perform such simulation-based power analysis
for multilevel models
(\citeproc{ref-arendStatisticalPowerTwolevel2019}{Arend \& Schäfer,
2019}; \citeproc{ref-brysbaertPowerAnalysisEffect2018}{Brysbaert \&
Stevens, 2018};
\citeproc{ref-debruineUnderstandingMixedEffectsModels2021}{DeBruine \&
Barr, 2021}; \citeproc{ref-greenSIMRPackagePower2016}{Green \& MacLeod,
2016}; \citeproc{ref-johnsonPowerAnalysisGeneralized2015}{Johnson et
al., 2015}; \citeproc{ref-kainPracticalGuidePower2015}{Kain et al.,
2015}; \citeproc{ref-kumleEstimatingPowerGeneralized2021}{Kumle et al.,
2021}; \citeproc{ref-lafitSelectionNumberParticipants2021}{Lafit et al.,
2021}; \citeproc{ref-zimmerSampleSizePlanning2023}{Zimmer et al.,
2023}). However, many of these tutorials focus on LMMs and the most
common study designs (see
\citeproc{ref-kumleEstimatingPowerGeneralized2021}{Kumle et al., 2021}
for a tutorial that also covers more advanced settings). This narrow
focus provides limited guidance for researchers using more complex study
designs, especially when little prior knowledge about plausible effect
sizes is available (see the discussion in
\citeproc{ref-kumleEstimatingPowerGeneralized2021}{Kumle et al., 2021}).
Simulation-based power analysis with GLMMs requires making a range of
assumptions about the model structure that should align with the
characteristics of the data being analyzed. Existing tutorials often
rely on heuristics for specifying variance components (e.g., the
standard deviation of random intercepts) or assume that results from
meta-analyses or data from pilot studies are available to determine
plausible values for all model parameters. However, in practice,
knowledge about those parameters from prior studies is often limited,
which makes specifying assumptions a practical challenge (see the
discussion in Maxwell et al.
(\citeproc{ref-maxwellSampleSizePlanning2008}{2008}) and Kumle et al.
(\citeproc{ref-kumleEstimatingPowerGeneralized2021}{2021})). We will
discuss a number of strategies on how to specify model parameters for
application-specific, tailored data simulations in a later chapter.

@@

\phantomsection\label{cell-fig-finalprecision}
\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{precision }\OtherTok{\textless{}{-}}\NormalTok{ sim\_result }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{pivot\_wider}\NormalTok{(}\AttributeTok{names\_from =}\NormalTok{ term, }\AttributeTok{names\_sep =} \StringTok{"\_"}\NormalTok{, }
    \AttributeTok{values\_from =}\NormalTok{ estimate}\SpecialCharTok{:}\NormalTok{p.value.equiv) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{group\_by}\NormalTok{(n\_subjects, n\_items) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{width =} \StringTok{\textasciigrave{}}\AttributeTok{conf.high\_b8=b2}\StringTok{\textasciigrave{}} \SpecialCharTok{{-}} \StringTok{\textasciigrave{}}\AttributeTok{conf.low\_b8=b2}\StringTok{\textasciigrave{}}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{summarise}\NormalTok{(}\AttributeTok{precision =} \FunctionTok{mean}\NormalTok{(width),}
    \AttributeTok{ci.lwr =} \FunctionTok{t.test}\NormalTok{(width)}\SpecialCharTok{$}\NormalTok{conf.int[}\DecValTok{1}\NormalTok{],}
    \AttributeTok{ci.upr =} \FunctionTok{t.test}\NormalTok{(width)}\SpecialCharTok{$}\NormalTok{conf.int[}\DecValTok{2}\NormalTok{], }
    \AttributeTok{.groups =} \StringTok{"drop"}\NormalTok{)}
\NormalTok{precision }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{mutate}\NormalTok{(}\FunctionTok{across}\NormalTok{(}\FunctionTok{c}\NormalTok{(n\_subjects, n\_items), factor)) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(n\_subjects, n\_items, }\AttributeTok{fill =}\NormalTok{ precision)) }\SpecialCharTok{+}
  \FunctionTok{geom\_tile}\NormalTok{() }\SpecialCharTok{+}
  \FunctionTok{geom\_text}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{label =} \FunctionTok{sprintf}\NormalTok{(}\StringTok{"\%.2f }\SpecialCharTok{\textbackslash{}n}\StringTok{ [\%.2f; \%.2f]"}\NormalTok{, }
\NormalTok{                                precision, ci.lwr, ci.upr)), }
    \AttributeTok{color =} \StringTok{"white"}\NormalTok{, }\AttributeTok{size =} \DecValTok{4}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{scale\_fill\_viridis\_c}\NormalTok{(}\AttributeTok{limits =} \FunctionTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\FloatTok{0.2}\NormalTok{), }\AttributeTok{direction =} \SpecialCharTok{{-}}\DecValTok{1}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{guides}\NormalTok{(}\AttributeTok{fill =} \FunctionTok{guide\_colourbar}\NormalTok{(}\AttributeTok{reverse =} \ConstantTok{TRUE}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

>>>>

\begin{tcolorbox}[enhanced jigsaw, leftrule=.75mm, left=2mm, title=\textcolor{quarto-callout-important-color}{\faExclamation}\hspace{0.5em}{Important}, colframe=quarto-callout-important-color-frame, breakable, rightrule=.15mm, coltitle=black, titlerule=0mm, arc=.35mm, toprule=.15mm, bottomtitle=1mm, colbacktitle=quarto-callout-important-color!10!white, opacitybacktitle=0.6, bottomrule=.15mm, toptitle=1mm, opacityback=0, colback=white]

@@

To our knowledge, existing approaches for sample size planning for GLMMs
have exclusively focused on planning for power. In Table 1, we review
available software packages that can be used to perform power analysis
for multilevel models in R {[}Version 4.3.3; R Core Team
(\citeproc{ref-R-base}{2024}){]}. Power analysis methods can be
categorized into formula-based, summary-statistics-based and
simulation-based methods
(\citeproc{ref-murayamaSummarystatisticsbasedPowerAnalysis2022}{Murayama
et al., 2022}). Formula-based methods rely on exact formulas to
calculate power directly. Summary-statistics-based methods use
statistical theory to approximate power based on formula-based methods
developed for simple t-tests. Simulation-based methods rely on
repeatedly simulating data with a known true effect size and estimating
power empirically, that is what percentage of simulated datasets
produces a significant p-value. Available formula-based and
summary-statistics-based software packages for multilevel models often
do not include GLMMs or are limited to simple designs
(\citeproc{ref-murayamaSummarystatisticsbasedPowerAnalysis2022}{Murayama
et al., 2022};
\citeproc{ref-westfallStatisticalPowerOptimal2014}{Westfall et al.,
2014}), making it necessary to build data simulations tailored
specifically to the study design. A number of tutorials have been
published describing how to perform such simulation-based power analysis
for multilevel models
(\citeproc{ref-arendStatisticalPowerTwolevel2019}{Arend \& Schäfer,
2019}; \citeproc{ref-brysbaertPowerAnalysisEffect2018}{Brysbaert \&
Stevens, 2018};
\citeproc{ref-debruineUnderstandingMixedEffectsModels2021}{DeBruine \&
Barr, 2021}; \citeproc{ref-greenSIMRPackagePower2016}{Green \& MacLeod,
2016}; \citeproc{ref-johnsonPowerAnalysisGeneralized2015}{Johnson et
al., 2015}; \citeproc{ref-kainPracticalGuidePower2015}{Kain et al.,
2015}; \citeproc{ref-kumleEstimatingPowerGeneralized2021}{Kumle et al.,
2021}; \citeproc{ref-lafitSelectionNumberParticipants2021}{Lafit et al.,
2021}; \citeproc{ref-zimmerSampleSizePlanning2023}{Zimmer et al.,
2023}). However, many of these tutorials focus on LMMs and the most
common study designs (see
\citeproc{ref-kumleEstimatingPowerGeneralized2021}{Kumle et al., 2021}
for a tutorial that also covers more advanced settings). This narrow
focus provides limited guidance for researchers using more complex study
designs, especially when little prior knowledge about plausible effect
sizes is available (see the discussion in
\citeproc{ref-kumleEstimatingPowerGeneralized2021}{Kumle et al., 2021}).
Simulation-based power analysis with GLMMs requires making a range of
assumptions about the model structure that should align with the
characteristics of the data being analyzed. Existing tutorials often
rely on heuristics for specifying variance components (e.g., the
standard deviation of random intercepts) or assume that results from
meta-analyses or data from pilot studies are available to determine
plausible values for all model parameters. However, in practice,
knowledge about those parameters from prior studies is often limited,
which makes specifying assumptions a practical challenge (see the
discussion in Maxwell et al.
(\citeproc{ref-maxwellSampleSizePlanning2008}{2008}) and Kumle et al.
(\citeproc{ref-kumleEstimatingPowerGeneralized2021}{2021})). We will
discuss a number of strategies on how to specify model parameters for
application-specific, tailored data simulations in a later section.

@@

\phantomsection\label{cell-fig-finalprecision}
\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{precision }\OtherTok{\textless{}{-}}\NormalTok{ sim\_result }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{pivot\_wider}\NormalTok{(}\AttributeTok{names\_from =}\NormalTok{ term, }\AttributeTok{names\_sep =} \StringTok{"\_"}\NormalTok{, }
    \AttributeTok{values\_from =}\NormalTok{ estimate}\SpecialCharTok{:}\NormalTok{p.value.equiv) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{group\_by}\NormalTok{(n\_subjects, n\_items) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{width =} \StringTok{\textasciigrave{}}\AttributeTok{conf.high\_b8=b2}\StringTok{\textasciigrave{}} \SpecialCharTok{{-}} \StringTok{\textasciigrave{}}\AttributeTok{conf.low\_b8=b2}\StringTok{\textasciigrave{}}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{summarise}\NormalTok{(}\AttributeTok{precision =} \FunctionTok{mean}\NormalTok{(width),}
    \AttributeTok{ci.lwr =} \FunctionTok{t.test}\NormalTok{(width)}\SpecialCharTok{$}\NormalTok{conf.int[}\DecValTok{1}\NormalTok{],}
    \AttributeTok{ci.upr =} \FunctionTok{t.test}\NormalTok{(width)}\SpecialCharTok{$}\NormalTok{conf.int[}\DecValTok{2}\NormalTok{], }
    \AttributeTok{.groups =} \StringTok{"drop"}\NormalTok{)}
\NormalTok{precision }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{mutate}\NormalTok{(}\FunctionTok{across}\NormalTok{(}\FunctionTok{c}\NormalTok{(n\_subjects, n\_items), factor)) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(n\_subjects, n\_items, }\AttributeTok{fill =}\NormalTok{ precision)) }\SpecialCharTok{+}
  \FunctionTok{geom\_tile}\NormalTok{() }\SpecialCharTok{+}
  \FunctionTok{geom\_text}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{label =} \FunctionTok{sprintf}\NormalTok{(}\StringTok{"\%.2f }\SpecialCharTok{\textbackslash{}n}\StringTok{ [\%.2f; \%.2f]"}\NormalTok{, }
\NormalTok{                                precision, ci.lwr, ci.upr)), }
    \AttributeTok{color =} \StringTok{"white"}\NormalTok{, }\AttributeTok{size =} \DecValTok{4}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{scale\_fill\_viridis\_c}\NormalTok{(}\AttributeTok{limits =} \FunctionTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\FloatTok{0.2}\NormalTok{), }\AttributeTok{direction =} \SpecialCharTok{{-}}\DecValTok{1}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{guides}\NormalTok{(}\AttributeTok{fill =} \FunctionTok{guide\_colourbar}\NormalTok{(}\AttributeTok{reverse =} \ConstantTok{TRUE}\NormalTok{)) }\SpecialCharTok{+}
  \FunctionTok{xlab}\NormalTok{(}\StringTok{"number of subjects"}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{ylab}\NormalTok{(}\StringTok{"number of items"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

### 2024-11-05 manuscript.qmd
Built site for gh-pages
fix precision result figure labels

@@

To our knowledge, existing approaches for sample size planning for GLMMs have exclusively focused on planning for power. In Table 1, we review available software packages that can be used to perform power analysis for multilevel models in `r cite_r()`. Power analysis methods can be categorized into formula-based, summary-statistics-based and simulation-based methods [@murayamaSummarystatisticsbasedPowerAnalysis2022]. Formula-based methods rely on exact formulas to calculate power directly. Summary-statistics-based methods use statistical theory to approximate power based on formula-based methods developed for simple t-tests. Simulation-based methods rely on repeatedly simulating data with a known true effect size and estimating power empirically, that is what percentage of simulated datasets produces a significant p-value.
Available formula-based and summary-statistics-based software packages for multilevel models often do not include GLMMs or are limited to simple designs [@westfallStatisticalPowerOptimal2014; @murayamaSummarystatisticsbasedPowerAnalysis2022], making it necessary to build data simulations tailored specifically to the study design. A number of tutorials have been published describing how to perform such simulation-based power analysis for multilevel models [@arendStatisticalPowerTwolevel2019; @lafitSelectionNumberParticipants2021; @zimmerSampleSizePlanning2023; @brysbaertPowerAnalysisEffect2018; @kumleEstimatingPowerGeneralized2021; @debruineUnderstandingMixedEffectsModels2021; @kainPracticalGuidePower2015; @greenSIMRPackagePower2016; @johnsonPowerAnalysisGeneralized2015]. However, many of these tutorials focus on LMMs and the most common study designs [see @kumleEstimatingPowerGeneralized2021 for a tutorial that also covers more advanced settings]. This narrow focus provides limited guidance for researchers using more complex study designs, especially when little prior knowledge about plausible effect sizes is available [see the discussion in @kumleEstimatingPowerGeneralized2021]. Simulation-based power analysis with GLMMs requires making a range of assumptions about the model structure that should align with the characteristics of the data being analyzed. Existing tutorials often rely on heuristics for specifying variance components (e.g., the standard deviation of random intercepts) or assume that results from meta-analyses or data from pilot studies are available to determine plausible values for all model parameters. However, in practice, knowledge about those parameters from prior studies is often limited, which makes specifying assumptions a practical challenge (see the discussion in @maxwellSampleSizePlanning2008 and @kumleEstimatingPowerGeneralized2021). We will discuss a number of strategies on how to specify model parameters for application-specific, tailored data simulations in a later chapter.

@@

Thus in our example, precision is defined as the (long-run) average width of a 95% CI for the probability contrast between experts with correct advice and experts without advice.
Of course, a lower width implies better precision.
Based on our simulation outcomes, we compute the precision estimate for each combination of `n_subjects` $\times$ `n_items` (including 95% CIs) and visualize the results with the following code.
```{r}
#| label: fig-finalprecision
#| fig-cap: "Simulation-based precision estimates (expected width of confidence intervals) including 95% confidence interval of the case study for different numbers of subjects and items, based on a confidence level of 0.95."
#| echo: true
precision <- sim_result %>%
  pivot_wider(names_from = term, names_sep = "_", 
    values_from = estimate:p.value.equiv) %>%
  group_by(n_subjects, n_items) %>%
  mutate(width = `conf.high_b8=b2` - `conf.low_b8=b2`) %>%
  summarise(precision = mean(width),
    ci.lwr = t.test(width)$conf.int[1],
    ci.upr = t.test(width)$conf.int[2], 
    .groups = "drop")
precision %>%
  mutate(across(c(n_subjects, n_items), factor)) %>%
  ggplot(aes(n_subjects, n_items, fill = precision)) +
  geom_tile() +
  geom_text(aes(label = sprintf("%.2f \n [%.2f; %.2f]", 
                                precision, ci.lwr, ci.upr)), 
    color = "white", size = 4) +
  scale_fill_viridis_c(limits = c(0, 0.3), direction = -1) +
  guides(fill = guide_legend(reverse=FALSE))
```
As should be the case, precision estimates in @fig-finalprecision increase  (i.e., average width of CI decreases) with the number of included subjects and items.
The CIs reported here indicate how precisely the expected width of the CI for our focal contrast was estimated by our simulation. Applying our simple heuristic of targeting an expected CI width that is smaller than 0.1, we see the same trade-off between the number of subjects and the number of items as with planning for power. We could either choose 100 subjects and 30 items or 250 subjects and 10 items. Note that our simple heuristic for determining sample size in the planning for precision scenario was quite liberal. This is reflected in the result that we would need a smaller sample size than in the planning for power scenario.
With a more conservative precision target, the result is generally the opposite: As a rule, precise parameter estimates usually require bigger samples than null hypothesis testing.

>>>>

date-modified: 2024-11-05

@@

To our knowledge, existing approaches for sample size planning for GLMMs have exclusively focused on planning for power. In Table 1, we review available software packages that can be used to perform power analysis for multilevel models in `r cite_r()`. Power analysis methods can be categorized into formula-based, summary-statistics-based and simulation-based methods [@murayamaSummarystatisticsbasedPowerAnalysis2022]. Formula-based methods rely on exact formulas to calculate power directly. Summary-statistics-based methods use statistical theory to approximate power based on formula-based methods developed for simple t-tests. Simulation-based methods rely on repeatedly simulating data with a known true effect size and estimating power empirically, that is what percentage of simulated datasets produces a significant p-value.
Available formula-based and summary-statistics-based software packages for multilevel models often do not include GLMMs or are limited to simple designs [@westfallStatisticalPowerOptimal2014; @murayamaSummarystatisticsbasedPowerAnalysis2022], making it necessary to build data simulations tailored specifically to the study design. A number of tutorials have been published describing how to perform such simulation-based power analysis for multilevel models [@arendStatisticalPowerTwolevel2019; @lafitSelectionNumberParticipants2021; @zimmerSampleSizePlanning2023; @brysbaertPowerAnalysisEffect2018; @kumleEstimatingPowerGeneralized2021; @debruineUnderstandingMixedEffectsModels2021; @kainPracticalGuidePower2015; @greenSIMRPackagePower2016; @johnsonPowerAnalysisGeneralized2015]. However, many of these tutorials focus on LMMs and the most common study designs [see @kumleEstimatingPowerGeneralized2021 for a tutorial that also covers more advanced settings]. This narrow focus provides limited guidance for researchers using more complex study designs, especially when little prior knowledge about plausible effect sizes is available [see the discussion in @kumleEstimatingPowerGeneralized2021]. Simulation-based power analysis with GLMMs requires making a range of assumptions about the model structure that should align with the characteristics of the data being analyzed. Existing tutorials often rely on heuristics for specifying variance components (e.g., the standard deviation of random intercepts) or assume that results from meta-analyses or data from pilot studies are available to determine plausible values for all model parameters. However, in practice, knowledge about those parameters from prior studies is often limited, which makes specifying assumptions a practical challenge (see the discussion in @maxwellSampleSizePlanning2008 and @kumleEstimatingPowerGeneralized2021). We will discuss a number of strategies on how to specify model parameters for application-specific, tailored data simulations in a later section.

@@

Thus in our example, precision is defined as the (long-run) average width of a 95% CI for the probability contrast between experts with correct advice and experts without advice.
Of course, a lower width implies better precision.
Based on our simulation outcomes, we compute the precision estimate for each combination of `n_subjects` $\times$ `n_items` (including 95% CIs) and visualize the results with the following code.
```{r}
#| label: fig-finalprecision
#| fig-cap: "Simulation-based precision estimates (expected width of confidence intervals) including 95% confidence interval of the case study for different numbers of subjects and items, based on a confidence level of 0.95."
#| echo: true
precision <- sim_result %>%
  pivot_wider(names_from = term, names_sep = "_", 
    values_from = estimate:p.value.equiv) %>%
  group_by(n_subjects, n_items) %>%
  mutate(width = `conf.high_b8=b2` - `conf.low_b8=b2`) %>%
  summarise(precision = mean(width),
    ci.lwr = t.test(width)$conf.int[1],
    ci.upr = t.test(width)$conf.int[2], 
    .groups = "drop")
precision %>%
  mutate(across(c(n_subjects, n_items), factor)) %>%
  ggplot(aes(n_subjects, n_items, fill = precision)) +
  geom_tile() +
  geom_text(aes(label = sprintf("%.2f \n [%.2f; %.2f]", 
                                precision, ci.lwr, ci.upr)), 
    color = "white", size = 4) +
  scale_fill_viridis_c(limits = c(0, 0.2), direction = -1) +
  guides(fill = guide_colourbar(reverse = TRUE)) +
  xlab("number of subjects") + ylab("number of items")
```
As should be the case, precision estimates in @fig-finalprecision increase  (i.e., average width of CI decreases) with the number of included subjects and items.
The CIs reported here indicate how precisely the expected width of the CI for our focal contrast was estimated by our simulation. Applying our simple heuristic of targeting an expected CI width that is smaller than 0.1, we see the same trade-off between the number of subjects and the number of items as with planning for power. We could either choose 100 subjects and 30 items or 250 subjects and 10 items. Note that our simple heuristic for determining sample size in the planning for precision scenario was quite liberal. This is reflected in the result that we would need a smaller sample size than in the planning for power scenario.
With a more conservative precision target, the result is generally the opposite: As a rule, precise parameter estimates usually require bigger samples than null hypothesis testing.
